method

### 2022-02-18 06_Paper/ER-ED/method.Rmd

for (i in 1:nrow(data_ER)) {

  if (data_ER$trigger[i] == 21) {

    data_ER$block[i] = "view_neu"

  } else if (data_ER$trigger[i] == 22) {

    data_ER$block[i] = "view_neg"

  } else if (data_ER$trigger[i] == 23 ) {

    data_ER$block[i] = "distraction"

  } else if (data_ER$trigger[i] == 24 ) {

    data_ER$block[i] = "distancing"

  } else if (data_ER$trigge[i] == 25 ) {

    data_ER$block[i] = "suppression"

  } else if (data_ER$trigger[i] == 26) {

    data_ER$block[i] = "choice"
  }
}

@@

# Bayes Factors
EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "view_neu"],
                                                                    y = EMG_view$Corr[EMG_view$block == "view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf

@@

colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGCorrView_con[1,1] <- "$View_{negative} - View_{neutral}$"

@@

# figure
FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

@@

# Bayes Factors
EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "view_neu"],
                                                                    y = EMG_view$Lev[EMG_view$block == "view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf

@@

colnames(EMGLevView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGLevView_con[1,1] <- "$View_{negative} - View_{neutral}$"

@@

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

>>>>

data_ER$block[data_ER$trigger == 21] <- "1_view_neu"
data_ER$block[data_ER$trigger == 22] <- "2_view_neg"
data_ER$block[data_ER$trigger == 23] <- "3_distraction"
data_ER$block[data_ER$trigger == 24] <- "4_distancing"
data_ER$block[data_ER$trigger == 25] <- "5_suppression"
data_ER$block[data_ER$trigger == 26] <- "6_choice"

@@

# Bayes Factors
EMGCorrView_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGCorrView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Corr[EMG_view$block == "1_view_neu"],
                                                                    y = EMG_view$Corr[EMG_view$block == "2_view_neg"],
                                                                    progress = FALSE, paired = TRUE))$bf

@@

colnames(EMGCorrView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGCorrView_con[1,1] <- "$View_{neutral} - View_{negative}$"

@@

# figure
FigEMGCorrViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

@@

# Bayes Factors
EMGLevView_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                       data = EMG_view,
                                       progress = FALSE)
EMGLevView_con$BF10 <- BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_view$Lev[EMG_view$block == "1_view_neu"],
                                                                   y = EMG_view$Lev[EMG_view$block == "2_view_neg"],
                                                                   progress = FALSE, paired = TRUE))$bf

@@

colnames(EMGLevView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
EMGLevView_con[1,1] <- "$View_{neutral} - View_{negative}$"

@@

# figure
FigEMGLevViewPilot=ggplot2::ggplot(EMG_view, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("1_view_neu", "2_view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Levator activity")

# effect of strategy on EMG

EMG_reg <- data_EMG %>%
  subset(data_EMG$block != "1_view_neu" & data_EMG$block != "6_choice")
EMG_reg$block <- as.factor(EMG_reg$block)

# corrugator
EMGCorrReg_aov <- afex::aov_ez(data = EMG_reg,
                              id = "ID",
                              dv = "Corr",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

# compute posthoc tests for within measures
EMGCorrReg_emm <- emmeans::emmeans(EMGCorrReg_aov$aov, specs = "block")

EMGCorrReg_con <- as.data.frame(pairs(EMGCorrReg_emm, adjust = "bonferroni"))

# Bayes Factors
EMGCorrReg_BF <- BayesFactor::anovaBF(formula = Corr ~ block,
                                      data = EMG_reg,
                                      progress = FALSE)

EMGCorrReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "2_view_neg"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "3_distraction"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf,
                         BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Corr[EMG_reg$block == "4_distancing"],
                                                                     y = EMG_reg$Corr[EMG_reg$block == "5_suppression"],
                                                                     progress = FALSE, paired = TRUE))$bf)

EMGCorrReg_con <- cbind(EMGCorrReg_con,
                        format(effectsize::t_to_eta2(t = EMGCorrReg_con$t.ratio,
                                                     df_error = EMGCorrReg_con$df,
                                                     ci = 0.95),digits = 2))

colnames(EMGCorrReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

EMGCorrReg_con[1,1] <- "$View_{negative} - Distraction$"
EMGCorrReg_con[2,1] <- "$View_{negative} - Distancing$"
EMGCorrReg_con[3,1] <- "$View_{negative} - Suppression$"
EMGCorrReg_con[4,1] <- "$Distraction - Distancing$"
EMGCorrReg_con[5,1] <- "$Distraction - Suppression$"
EMGCorrReg_con[6,1] <- "$Distancing - Suppression$"

# figure
FigEMGCorrRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Corr))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Corrugator activity")

EMGLevReg_aov <- afex::aov_ez(data = EMG_reg,
                              id = "ID",
                              dv = "Lev",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

# compute posthoc tests for within measures
EMGLevReg_emm <- emmeans::emmeans(EMGLevReg_aov$aov, specs = "block")

EMGLevReg_con <- as.data.frame(pairs(EMGLevReg_emm, adjust = "bonferroni"))

# Bayes Factors
EMGLevReg_BF <- BayesFactor::anovaBF(formula = Lev ~ block,
                                      data = EMG_reg,
                                      progress = FALSE)

EMGLevReg_con$BF10 <- c(BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "2_view_neg"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "3_distraction"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf,
                        BayesFactor::extractBF(BayesFactor::ttestBF(x = EMG_reg$Lev[EMG_reg$block == "4_distancing"],
                                                                    y = EMG_reg$Lev[EMG_reg$block == "5_suppression"],
                                                                    progress = FALSE, paired = TRUE))$bf)

EMGLevReg_con <- cbind(EMGLevReg_con,
                       format(effectsize::t_to_eta2(t = EMGLevReg_con$t.ratio,
                                                    df_error = EMGLevReg_con$df,
                                                    ci = 0.95),digits = 2))

colnames(EMGLevReg_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

EMGLevReg_con[1,1] <- "$View_{negative} - Distraction$"
EMGLevReg_con[2,1] <- "$View_{negative} - Distancing$"
EMGLevReg_con[3,1] <- "$View_{negative} - Suppression$"
EMGLevReg_con[4,1] <- "$Distraction - Distancing$"
EMGLevReg_con[5,1] <- "$Distraction - Suppression$"
EMGLevReg_con[6,1] <- "$Distancing - Suppression$"

# figure
FigEMGLevRegPilot <- ggplot2::ggplot(EMG_reg, aes(x = block, y = Lev))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("2_view_neg", "3_distraction", "4_distancing", "5_suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Levator activity")
